\sysfull

### 2018-04-11 paper/intro.tex
wrapfig for reasonable fig size

\begin{figure}
	\includegraphics[width=0.95\columnwidth]{figures/coalescing-is}
    \caption{\label{fig:coalesce}\textbf{An execution of three
statically-defined tasks without (top) and with (bottom) dynamic
coalescing.} Task coalescing at runtime reduces time and energy overhead in
task-based intermittent programming models by performing fewer commits and
buffering updates to non-volatile (NV) variables in volatile (V) memory.}
\end{figure}

>>>>

\begin{wrapfigure}{t!}{0.5\textwidth}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/coalescing-is}
    \caption{\textbf{An execution of three
statically-defined tasks without (top) and with (bottom) dynamic
coalescing.} Task coalescing at runtime reduces time and energy overhead in
task-based intermittent programming models by performing fewer commits and
buffering updates to non-volatile (NV) variables in volatile (V) memory.}
    \label{fig:coalesce}
\end{wrapfigure}
